---
title: "Computational Complexity"
author: "Keshav Padiyar Manuru"
date: "12/10/2020"
output: pdf_document
---

# Exercise 1

## a

$\sum_{i=2}^n \binom{i}{2} = \binom{n+i}{3}$

### proof:

$\sum_{i=2}^n \binom{i}{2} = \sum_{i=1}^n \frac{2!}{0! 2!} + \frac{3!}{1!2!}+ ...$

$= \sum_{i=2}^n \frac{i!}{2!(i-2)!}$

$= \sum_{i=2}^n \frac{i (i-1) (!-2)!}{2!(i-2)!}$ 

$= \sum_{i=2}^n \frac{i (i-1)}{2}$ 

$= \sum_{i=2}^n \frac{i^2-i}{2}$ 

$= \sum_{i=1}^n \frac{i^2}{2}-1-\sum_{i=1}^n \frac{i}{2}-1$

$=\frac{n(n+1)(2n+1)}{6 *2} - \frac{n(n+1)}{2 * 2}$

$=\frac{n(n+1)(2n-2)}{6*2}$

$=\frac{n(n+1)(n-1)}{6}$

$=\frac{(n+1) n (n-1)}{3*2}$

multiply and divide by $(n-2)!$

$=\frac{(n+1) n (n-1) (n-2)!}{3*2 (n-2)!}$

$=\frac{(n+1) n (n-1) (n-2)!}{3*2 (n+1 - 3)!}$

$=\frac{(n+1) n (n-1) (n-2)!}{3! (n+1 - 3)!}$

$= \binom{n+i}{3}$

## b

$\sum_{i=1}^n i^3 = (\frac{n(n+1)}{2})^2$

### proof:

expanding  $\sum_{i=1}^n i^4 - (i-1)^4$

$\sum_{i=1}^n i^4 - (i-1)^4 = n^4 - (n-1)^4 + (n-1)^4 - (n-2)^4 + ....+3^4-2^4+2^4-1^4+1^4-0^4$

$\sum_{i=1}^n i^4 - (i-1)^4 = n^4$ ..... $(1)$ As remaining terms gets canceled with each others.

lets solve  $i^4 - (i-1)^4$

$i^4 - (i-1)^4 = i^4 - [(i-1)^2(i-1)^2]$

$= i^3 - 6i^2 + 4i - 1$

$and, \sum_{i=1}^n  i^4 - (i-1)^4  = \sum_{i=1}^n 4i^3 - \sum_{i=1}^n 6i^2+ \sum_{i=1}^n 4i -\sum_{i=1}^n 1$

$\sum_{i=1}^n i^4 - (i-1)^4 = 4\sum_{i=1}^n i^3 - \frac{6 n (n+1) (2n+1)}{6} + \frac{4 n (n+1)}{2} - n$

by $(1)$

$4\sum_{i=1}^n i^3 - \frac{6 n (n+1) (2n+1)}{6} + \frac{4 n (n+1)}{2} - n =  n^4$

$4\sum_{i=1}^n i^3  =  n^4 + \frac{6 n (n+1) (2n+1)}{6} - \frac{4 n (n+1)}{2} + n$

$4\sum_{i=1}^n i^3  =  n^2(n+1)^2$

$\sum_{i=1}^n i^3  =  \frac{n^2(n+1)^2}{4}$

$\sum_{i=1}^n i^3  =  (\frac{n(n+1)}{2})^2$

# Exercise 2

## a

$(x^2+ 3x+ 1)^3 = o(x^6)$

for $f(n) = o(g(n))$

$\lim_{n \to \inf} \frac{f(n)}{g(n)} = 0$

for $f(n)$ expand $(x^2+ 3x+ 1)^3$

$f(n) = x^6+9x^5+30x^4+45^x3+30x^2+9x+1$

$g(n) = x^6$ 

since  $\lim_{x \to \inf} (\frac{x^6+9x^5+30x^4+45^x3+30x^2+9x+1}{x^6}) \ne 0$ 

ANS (a): **FALSE**

## b

$\frac{\sqrt{x}+1}{2} = o(1)$

for $f(n) = o(g(n))$

$\lim_{n \to \inf} \frac{f(n)}{g(n)}= 0$

since  $\lim_{x \to \inf} (\frac{\sqrt{x}+1}{2 * 1}) \ne 0$ 

ANS (b): **FALSE**

## c

$e^\frac{1}{x} = o(1)$

for $f(n) = o(g(n))$

$\lim_{n \to \inf} \frac{f(n)}{g(n)} = 0$

since  $\lim_{x \to \inf} \frac {e^\frac{1}{x}}{1} \ne 0$ 

$e^\frac{1}{\inf} = e^0 = 1$

ANS (c): **FALSE**

## d

$\frac{1}{x} = o(1)$

for $f(n) = o(g(n))$

$\lim_{n \to \inf} \frac{f(n)}{g(n)} = 0$

since  $\lim_{x \to \inf} \frac {\frac{1}{x}}{1} =  0$ 

ANS (d): **TRUE**

## e

$x^3(\log(\log{x}))^2 = o(x^3 \log{x})$

for $f(n) = o(g(n))$

$\lim_{n \to \inf} \frac{f(n)}{g(n)} = 0$

$\lim_{x \to \inf} \frac{x^3(\log(\log{x}))^2}{x^3 \log{x}}$

let us consider $y = \log{x}$

then 

$\lim_{y \to \inf} \frac{(\log{y})^2}{y} = 0$

ANS (e): **TRUE**

## f
$\sqrt{\log{x}+1} = \Theta{(\log\log{x})}$

for $\Theta{(n)}$

$c1g(n)\le f(n) \le c2g(n)$

let us consider $y = \log{x}$

$\sqrt{y+1} = \Theta{(\log{y})}$

$\sqrt{y+1} \approx \sqrt{y}$

since $\frac{d\sqrt{y}}{dy} > \frac{d\log{y}}{dy}$ 

$\sqrt{\log{x}+1} > c2(\log\log{x})$ 

ANS (f): **FALSE**

## g

$2+sin{x} = \Omega{(1)}$

for $\Omega{(n)}$

$f(n) \ge c g(n)$

since $\sin(x)$ ranges from -1 to 1

$2+sin{x} \ge 1$ and $2+sin{x} \ge c(1)$

ANS (g): **TRUE**

## h

$\frac{\cos{x}}{x} = O{(1)}$

for $O{(n)}$

$f(n) \le c g(n)$

since $\lim_{x \to \inf} \frac{\cos(x)}{x} \approx 0, x\ne0$

$\frac{\cos(x)}{x} \le c * 1$

ANS (h): **TRUE**

## i
$\int_{4}^x \frac{dt}{t} = O(\ln{x})$

for $O{(n)}$

$f(n) \le c g(n)$

$\int_{4}^x \frac{dt}{t} = \ln{t}|_{4}^x = \ln{x} - \ln{4} \approx \ln{x}$

$\int_{4}^x \frac{dt}{t} \le c (\ln x)$

ANS (i): **TRUE**

## j

$\sum_{j=1}^x \frac {1}{j^2} = O(1)$

for $O{(n)}$

$f(n) \le cg(n)$

$\sum_{j=1}^{\inf}\frac{1}{j^2} = \frac{\pi^2}{6}$

$\sum_{j=1}^x \frac{1}{j^2}<\frac{\pi^2}{6}$

$\sum_{j=1}^x \frac{1}{j^2}\le c*(1)$

ANS (j): **TRUE**

## k

$\sum_{j=1}^n 1 = \Theta(x)$

for $\Theta{(n)}$

$c1g(n)\le f(n) \le c2g(n)$

$\sum_{j=1}^x 1 = x$

$c1(x)\le \sum_{j=1}^x 1 \le c2(x)$

ANS (k): **TRUE**

## l

$\int_{0}^x e^{-t^2} dt = O(1)$

for $O{(n)}$

$f(n) \le c g(n)$

$\int_{-\inf}^{\inf} e^{-t^2} dt = \sqrt{\pi}$

$\int_{0}^x e^{-t^2}dt < \sqrt{\pi}$

$\int_{0}^x e^{-t^2}dt < c*(1)$

ANS (k): **TRUE**

# Exercise 3

## a

**ANS**: ${e^{\log{n^3}}}, n{^{3.01}}, 2^{\sqrt{n}},{2^{n^2}}$

## b

**ANS**: $1+{\log^3{n}},{n^{{1.6}}},{n^{\log n}},{\sqrt{n!}}$

## c

**ANS**: ${(\log\log n)^2}, n^3\log{n}, (n+4)^9, 2^{n\sqrt{n}}$

## d

**ANS**: $({\frac{1}{3}})^n, 17, {\log \log n}, {\log n}, 2^{\sqrt{\log n}} ,{\sqrt{n}}, {{\sqrt{n}}{(\log n)}}, {\frac{n}{logn}}, 2n, {{(\frac{3}{2})}^n},(\frac{n}{2})^{\log n}$

# Exercise 4

## a 

$\binom{2}{3}^n+\sum_{i=1}^n{\sin^2 n}+n^2+\ln{(\sum_{i=1}^n{\binom{n}{i}})}$

$\frac{d{\binom{2}{3}^n}}{dn} = n *\binom{2}{3}^{n-1}$

$\frac{d{\sum_{i=1}^n{\sin^2 n}}}{dn} = \sum_{i=1}^n{\sin2n}$

$\frac{dn^2}{dn} = 2n$

$\frac{d{\ln{(\sum_{i=1}^n{\binom{n}{i}})}}}{dn} = \frac{d{\ln{2^n}}}{dn} = \frac{d{\frac{\log_{2}{{2}^{n}}}{\log_2e}}}{dn} = \frac{d{\frac{n}{log_2e}}}{dn} = \frac{1}{\log_2e}$

**ANS**: $n *\binom{2}{3}^{n-1}+\sum_{i=1}^n{\sin2n}+2n+\frac{1}{\log_2e}$

## b

$\binom{n}{2}+\sum_{1}^n{\log n}+n^2{\sin n}$

$\frac{d\binom{n}{2}}{dn} = \frac{d{\frac{n(n-1)}{2}}}{dn} = \frac{2n-1}{2}$

$\frac{d\sum_{1}^n{\log n}}{dn} = \sum_{1}^n{\frac{1}{n}}$

$\frac{dn^2{\sin n}}{dn} = 2n{\sin n}+n^2{\cos n}$

**ANS**: $\frac{2n-1}{2} + \sum_{1}^n{\frac{1}{n}} +2n{\sin n}+n^2{\cos n}$

# Exercise 5

**ANS**: **d** $2^{\sqrt{n}}$ grows faster than $n^2$ and slower than $\sqrt{2^n}$

# Exercise 6

Outer Loop: $0(\sqrt{n})$

Inner Loop: $0(\sqrt{n})$

**ANS**: $O(n)$

# Exercise 7

Outer Loop: $0({n})$

1st Inner Loop: $0({n})$

2nd Inner Loop: $0({n})$

**ANS**: $O(n^3)$

# Exercise 8

**ANS**

$2n$ multiplication operations need to be done in the worst case

$n$ summations

# Exercise 9

Outer Loop: $0({n-1}) \approx O(n)$

1st Inner Loop: $0({n-1}) \approx O(n)$

2nd Inner Loop: $0({n-1}) \approx O(n)$

**ANS**: $O(n^3)$

# Exercise 10

Outer Loop: $0({n-1}) \approx O(n)$

1st Inner Loop: $0({n/2})$

2nd Inner Loop: $0({n/2})$

$ = O(n)*((O({n/2})+O(n/2)))$

**ANS**: $O(n^2)$

# Exercise 11

Outer Loop: $0({n-1}) \approx O(n)$

1st Inner Loop: $0({n/2})$

2nd Inner Loop: $0({n/2})$

$= O(n)*((O({n/2})*O(n/2))) = O(n^3/4) \approx O(n^3)$

**ANS**: $O(n^3)$

# Exercise 12

## a $\Theta(n^2) summations$
```{r}
M <- matrix(c(1,2,3,4,5,6,7,8,9), nrow = 3)

sum = 0

for (i in 1: nrow(M)){

    for (j in 1:i){
    
    sum = sum + M[i,j]
    
  }
}
sum
```
## b $\Theta{(n)} summations$
```{r}
M <- matrix(c(1,2,3,4,5,6,7,8,9), nrow = 3)

v = 0

for (i in 1:nrow(M)){
 
 v = v + sum(M[i,1:i])
 
}

v

```
## c $O(1) summations$
```{r}
M <- matrix(c(1,2,3,4,5,6,7,8,9), nrow = 3)

sum(M[lower.tri(M,diag = TRUE)])
```


# Exercise 13

## a

**ANS**: $O(2^{n}-1)$ and the function returns $2^{n-1}$ values for $n>1$ 

## b

**ANS**: $O(n)$ and the function returns$2^{n-1}$ values for $n>1$ 

## c

**ANS**: $O(n)$ and the function returns $1$ 

## d

**ANS**: $O(n)$ and the function returns $n$ 

# Exercise 14

**ANS**: $O(n^3)$

# Exercise 15

**ANS**: $O(2^n)$ and the function returns $n$































