---
title: "SwedishKoladaAPI"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SwedishKoladaAPI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The SwedishKoladaAPI package is developed to access the data from Kolada Web API. SwedishKoladaAPI connects to the given URL, pulls the data and parses the data to data.frame. For more information on Kolada API, refer "https://www.kolada.se/"

getKoladaAPIData() function in the package should be used to access API and fetch data. The function takes below inputs and returns a data.frame.

**l_kpi** : Required KPI Code
 
```{r echo=FALSE, results='hold'}
df = data.frame(KPI_Code = c("N00002","N00011","N00014"),
KPI_Name = c("Personnel costs as a proportion of operating costs, share (%)","Income equalization, allowance / fee, SEK / inv. 1 Nov fg year","Adjustment contribution / fee, SEK / inv (2005-)") )

knitr::kable(df, caption = "Sample KPIs")
```
For More KPIs refer "http://api.kolada.se/v2/kpi?all"

**l_m** : Required Municipality Code
```{r echo=FALSE, results='hold'}
df = data.frame(Municipality_Code = c("1480","0580","1281","1280","0581","0180","0001","2480","0380"), Municipality_Name = c("Goteborg","Linkoping","Lund","Malmo","Norrkoping","Stockholm","Stockholms lans landsting","Umea","Uppsala") )

knitr::kable(df, caption = "Sample Municpalities")
```
For More Municipalities and their codes refer "http://api.kolada.se/v2/municipality?all"

 **l_year** : Year for which the data to be observed

 **url** : If data to be fetched from a specific URL
 
 Also, the function has 2 features:
 
 1. Given only the first 3 parameter value, the function will fetch the data for given kpi, municipality and years
 
```{r}
library(SwedishKoladaAPI)

final_data = getKoladaAPIData(l_m = "0180,0581,0580",
                     l_kpi = "N01951,N61714",
                     l_year = "2018,2019,2020"
                     )

head(final_data,10)
```
 2. User can also give required URL to get the data.
 
```{r}
library(SwedishKoladaAPI)

final_data = getKoladaAPIData(
                     url = "http://api.kolada.se/v2/municipality?all")

head(final_data,10)
```
