---
title: "Implementation of Linear Regression Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.show = "hold",
  fig.width = 5,
  fig.height = 5
)
```
linearRegression is a R package, it contains the implementation of Linear Regression class (linreg()), which is similar to the existing lm() class. The linreg takes two arguements - 1. Formula, 2. Data.
Formuala: It is the object that contains the relation between the dependent and Independent variables of a desired data set.
Data: It is the data set on which the regression to be performed, and contains the variables mentioned in the formula.

linreg function returns and object of S3 class. Below are the Methods associated with linreg class:

1. print(): Prints the regression formula and data along with the coefficients.

1. Summary(): Returns a similar printout as printed for lm objects, but includes only the coefficients with 
                        their standard error, t-value and p-value as well as the estimate of residual variance
                        and the degrees of freedom in the model.

1. coef(): Returns the coefficients as a named vector.

1. resid(): Returns the vector of residuals e.

1. pred(): Returns the predicted values y.

1. plot(): Plots the two plots (1. Residuals vs Fitted, 2. Scale-Location) using ggplot2.

## Linear Regression
In statistics, linear regression is a linear approach to modeling the relationship between a scalar response and one or more explanatory variables. The case of one explanatory variable is called simple linear regression. Refer [Wikipedia] (https://en.wikipedia.org/wiki/Linear_regression).

## Implementation and Usage
For demonstration of the usage of the package, we are considering Iris data set and relation between the Petal.Length and Species will be observed.

Considering the formula: **Petal.Length~Species**
```{r setup}
library(linearRegression)
data(iris)
model = linreg(formula = Petal.Length~Species, data = iris)
```

Observing the output of each methods

1. print()

```{r}
print(model)
```

2. summary()
```{r}
summary(model)
```

3. coef()
```{r}
coef(model)
```

4. resid()
```{r}
resid(model)
```

5. pred()
```{r}
pred(model)
```

6. plot()
```{r}
plot(model)
```